---
title: "Avinash_Sriram_HW6"
author: "Avinash Sriram"
date: "`r Sys.Date()`"
output: pdf_document
---

# Question 1
# The approach for this problem was to get the z-score for the problem then use the pnorm function to get the probability
```{r}
pop_mean <- 256000 / 16000.00
sample_size <- 34
pop_sd <- sqrt(256000 / (16000)^2)

sample_mean <- 16.01

z_score <- (sample_mean - pop_mean) / (pop_sd / sqrt(sample_size))

q1_prob <- pnorm(z_score, lower.tail = FALSE)

print(signif(q1_prob), digits = 4)
```

# Question 2
# The approach for this problem was get the sample mean and standard deviation and apply it. I manipulated the diff norm() methods to help get the solutions
```{r}
# Part (A)
mu <- 8.2
pop_sd <- 1
sample_size <- 60
sample_sd <- 1 / sqrt(60)
sample_mean <- 8.2

print(signif(sample_mean), digits = 4)
print(signif(sample_sd), digits = 4)

# Part (B)
percentile_z_score <- qnorm(0.9)
sample_mean <- (percentile_z_score * sample_sd) + mu
print(signif(sample_mean), digits = 5)

# Part (C)
one_sd <- pnorm(1) - pnorm(-1)
two_sd <- pnorm(2) - pnorm(-2)
three_sd <- pnorm(3) - pnorm(-3)

print(signif(one_sd), digits = 4)
print(signif(two_sd), digits = 4)
print(signif(three_sd), digits = 4)

# Part (D)
print("The empirical rule (68-95-99.7) would allow for part 2c 
      to be completed without any work. This is because one 
      standard deviation (sd) would result in approximately 68% 
      of the data falling within in it, 95% of the data for 
      2 standard deviations, and 99.7% for three.")
```

# Question 3
# The approach for this problem was similar to that of problem 2. I manipulated the mean and standard deviation values for parts C and D as it was asking for the total of the entire sample so I multiplied by 75
```{r}
# Part (A)
# CLT
sample_mean <- 5 * 0.5
pop_sd <- sqrt(sample_mean * (1 - 0.5))
sample_sd <- pop_sd / sqrt(75)

z_score <- (2.25 - sample_mean) / sample_sd

prob <- pnorm(z_score)

print(signif(prob), digits = 4)

# Part (B)
percentile_mean <- qnorm(.9, sample_mean, sample_sd)
print(signif(percentile_mean), digits = 5)

# Part (C)
prob <- pnorm((200 / 75), sample_mean, sample_sd)
print(signif(prob), digits = 4)

# Part (D)
percentile_prob <- qnorm(0.9, 75 * sample_mean, 75 * sample_sd)
print(percentile_prob)
```

# Question 4
# For this one, I used the pexp method for part A and then used CLT for part B and compared the probabilities
```{r}
# Part (A)
lambda <- 1 / 2
prob <- pexp(2.5, lambda, lower.tail = FALSE)
print(signif(prob), digits = 4)

# Part (B)
# CLT
sample_mean <- 2
sd <- 2 / sqrt(80)
z_score <- (2.5 - sample_mean) / (sd)
prob <- pnorm(z_score, lower.tail = FALSE)
print(signif(prob), digits = 3)

# Part (C)
print("Part A only looks at one specific individual whereas 
      Part B looks at the entire customer set. This would result 
      in a difference in probabilities as the 80 customers would 
      be having less variability than the individual therefore 
      would result in a lower probability.")
```

# Question 5
# The approach for this question was to do the problem by hand at first then translate it to R
```{r}
p <- 22 / 30
n <- 30
z <- qnorm(0.975)
upper <- p + z * (sqrt((p * (1 - p)) / n))
lower <- p - z * (sqrt((p * (1 - p)) / n))
confidence_interval <- c(lower,upper)
print(signif(confidence_interval), digits = 4)
```
